\documentclass{proc}

\begin{document}

\title{Discovering the population in Skyrim}

\author{Botao Han}

\maketitle

\section{Introduction}

There are eleven years since Bethesda released Skyrim. Skyrim provided a big and epic stage for players to explore. Many players left beautiful yet immersive experiences in Skyrim, but few of them fully explore the diverse NPCs in the game. I plan to use the data from UESP(The Unofficial Elder Scroll Page) to fully explore the diversity of the NPCs, and uncover the colorful people in Skyrim.

\section{Describe your project in one sentence}

Based on the data from UESP, I will visualize the characteristic of NPCs in Skyrim and show the distribution of each property.

\section{What type of project is this and why?}

Experiment

\section{Who is the audience for this project? How does it meet their needs? What happens if their needs remain unmet?}

The project aims to present the diversity and property distribution to the player who is very interested in Skyrim and doesn't have further investigation. The visualization that will propose in this project will let Skyrim fans have a deeper understanding of the game, thus providing a sturdy background to learn about the lore in Skyrim. Adopting the presented data may cause the viewer to miss viewing the diverse world developer created.	

\section{What is your approach and why do you think it’s cool and will be successful?}

\begin{enumerate}
\item Currently there is none single visualization about the diversity of NPCs in Skyrim.
\item The information collected are not limited to gender and race, the visualization can also show the city he/she lives and his/her class and more.
\end{enumerate}


\section{In the best-case scenario, what would be the impact statement (conclusion statement) for this project?  } 

The good scenario is that the visualization can let more Skyrim fans or even people who haven't played Skyrim have an interest in the game and want to learn more about the world behind Skyrim.


\section{List all major milestones for this project.}

\begin{enumerate}
  \item getting data from UESP
  \item get the properties of each NPC
  \item try different graph that is most intuitive for viewers

\end{enumerate}

\section{What obstacles do you anticipate?}

\subsection{Major obstacles} 

\begin{itemize}
  \item The main problem here is to choose which graph can have most intuitive effect towards viewers.
\end{itemize}

\subsection{Minor obstacles}

\begin{itemize}
  \item The minor problem is to select between different choices like if should make the elements interactable or the choice of color theme.
\end{itemize}

\section{What additional resources do you need to complete this project?}

\begin{itemize}
  \item May need further information from UESP to present more interesting information.
 \end{itemize}

\section{When / How do you know if you have succeeded in this project?}

I think that this research will have impact on viewers and attract more viewers to have interest in Skyrim.

%\bibliographystyle{abbrv}
\end{document}
